---
title: "Hello World"
output: html_document
---

# Introduction

This is a sample R Markdown document demonstrating how to combine text, R code, and output into a single report. R Markdown allows for reproducible research by embedding code directly within the narrative.

## Markdown Basics

You can use various Markdown syntax for formatting:

*   **Bold text** with double asterisks.
*   *Italic text* with single asterisks or underscores.
*   Code snippets like `print("Hello, R Markdown!")` with backticks.

## R Code Chunk

Here's an R code chunk.
```{r}
print("hello world")
```

Using `echo=FALSE` option in the chunk header means the R code itself will not be displayed in the output, only its results.
```{r echo=FALSE}
print("hello world")
```

Here's a plot.
```{r}
# Load the ggplot2 library
library(ggplot2)

# Create a sample data frame
data <- data.frame(
  x_value = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
  y_value = c(2, 4, 5, 4, 6, 7, 8, 9, 10, 12),
  category = factor(c("A", "A", "B", "A", "B", "A", "B", "B", "A", "B"))
)

# Create the scatter plot
ggplot(data, aes(x = x_value, y = y_value, color = category)) +
  geom_point(size = 3) + # Add points and set their size
  labs(
    title = "Scatter Plot of X vs Y by Category",
    x = "X-axis Label",
    y = "Y-axis Label",
    color = "Category" # Legend title for color
  ) +
  theme_minimal() # Use a minimalist theme
```